\textbf{AES} - Symmetric encryption standard.

\textbf{Client} - The program that will be used by users which connects to a 
turtlenet server.

\textbf{FaceBook} - A social networking website designed to make the world more 
open and to connect people together in a simple format.

\textbf{SocialNetwork} - A website build around facillitating social
interaction.

\textbf{Privacy} - Personal information being known to only those whom you choose 
to inform of it.

\textbf{QrCode} - QR stands for Quick Response.  Used to store data it is a form 
of 2D bar code, It was designed to be easy to read from low quality photographs.

\textbf{RSA} - An asymmetric encryption algorithm.

\textbf{Server} - A computer running the turtlenet server which allows clients
to connect to it.

\textbf{ServerOperator} - The owners and engineers responsible for running 
Turtlenet servers.

\textbf{Category} - We allow our users to create `Categories', and place one or 
more users into one or more categories. These sets of users are used to speed up 
reptitive actions such as allowing all of your friends permission to view 
something, by instead allowing the user to allow the category `friends' to view 
it.

\textbf{Relation} - Two users must know each others public keys in order to 
communicate. We say that two users who possess each others keys are in a 
`relation'. This is done because it is a situation we talk about often, and it 
helps to have a word for it.

\textbf{Parameterized Query} - A precompiled query lacking important information 
for the values of parts of it. These are used to protect against SQL injection 
and to provide a greater degree of abstraction from the database for the rest of 
the system.

\textbf{Onion Routing} - A manner of routing traffic in a network with the goal 
of obscuring from the recipient who the sender was. This is achieved by routing 
it through a number of intermediaries, none of which have access to both who sent 
the traffic, and the plaintext traffic.
\footnote{See http://en.wikipedia.org/wiki/Onion\_routing for more information.}

\textbf{Tor} - An implementation of onion routing.
