\todo[noline]{pretty dataflow diagrams}
\textbf{Creating an account} is done by generating an RSA keypair, and choosing
a name. An unencrypted (but signed) message is then posted to the server
associating that keypair with that name. In this way, by knowing the public key
of someone, you may discover their name in the service, but not vice versa.\\

\textbf{Connecting for the first time} Every unencrypted message stored on the
server is downloaded(signed nicknames and nothing more). At this time the local
database contains only signed messages
claiming usernames. The public keys are not provided, these are of use only when
you learn the public key behind a name. The rationale for not providing public
keys is provided in the section regarding adding a friend. Messages posted
after your name was claimed will require downloading too, as once you claim a
name people may send you messages. It's worth noting that messages from before
you connected for the first time are now downloaded because they can not have
been sent to you (with a complient client) if someone retroactivly grants you
permission to view something they publish it as a new message with an old
timestamp; the sole exception to this is when you connect using a new device,
in which case all messages since you first claimed a name will be downloaded.\\

\textbf{Connecting subsequently} The client requests every message stored on the
server since the last time they connected up to the present. Decryptable
messages are used to update the local DB, others are discarded.\\

\textbf{Continued connection} During a session the client requests updates from
the server every 0.5-5 seconds (configurable by the user).\\

\textbf{Adding a friend} is performed by having a friend email (or otherwise
transfere) you their public key. This is input to the client, and it finds their
username (via public posting that occured when registering). You may now
interact with that person. They may not interact with you until they recieve
your public key. Public key transferal will be performed via exchaning plaintext
base64 encoded strings, or QR codes. The user will be prompted, after retrieving
the username of the user, to catagorise them.\\

\textbf{Talking with a friend or posting on your wall} is achieved by writing
a message, signing it with your private key, and encrypting one copy of it with
each of the recipiants public keys before posting it to the server. The client
prevents one from posting a message to someones public key if they have not
claimed a nickname.\\

\textbf{Posting to a friends wall, commenting and liking} may be requested by
sending a EPOST/CMNT/LIKE message to the friend (upon whose wall/post you are
posting, commenting or liking), when that friend logs in they will recieve your
request and may confirm or deny it. If they confirm then they take your (signed)
message and transmit it to each of their friends as previously described. Given
that authentication is entirely based on crypto signatures it doesn't matter
that your friend relays the message.This is required because it is impossible
for one to know who is able to see the persons wall, post, or comment upon which
you seek to post, like, or comment.
