alt.anonymous.messages is a newsgroup\footnote{It may be accessed, without an
installed Usenet client, through several websites providing an interface to it,
one such website is Google Groups, and may be accessed here:
https://groups.google.com/forum/\#!forum/alt.anonymous.messages} to which people
publicly post encrypted messages. In order to retrieve messages a recipient
downloads all new messages and attempts to decrypt them all, those which they
are able to decrypt are read, and others ignored.

This type of system is known as a 'shared mailbox', and is often not used by
hand, but by mix network servers, which provide high-latency email forwarding,
and handle the encryption on behalf of the users. Mix-networks massively slow
timing-based traffic confirmation because they cache a large number of messages
before sending them all out at once in a random order\cite{mixnetOperation}.

This system provides the property we are seeking: concealing who talks with whom
on our network, even from the server itself. This property is ensured by the
fact that the server cannot tell who reads a specific message, even though it
knows which IP uploaded it. It also introduces a huge amount of overhead, in the
form of downloading everyone else's messages as well as ones own.

Mix networks however have some serious issues, and misconfiguration easily
allows for traffic correlation\cite{mixnet}, albeit not confirmation (without a
large sample size). Furthermore mix networks only function if the operator is
trusted, this is unacceptable against our threat model. For these reasons we will not
use the idea of mix networks.

We have identified the method of operation of shared mailboxes as the basis for
our communications protocol, and will build a social network on top of this 
concept.
