\subsection{Posts, and functions thereof}
Facebook allows a user to post on their wall or friend's wall (if they are
friens with the facebook user). Posts may contain: text, images, videos, or any
combination thereof.

A user posting a post may do the following:
\begin{itemize}
\item delete their own post
\item rewrite their own post
\item decide who may view a post, the options are as follows:
    \begin{itemize}
    \item public
    \item private
    \item only-me
    \item friends only
    \item friends of friends
    \item \ldots \todo{does FB allow sharing to one or two specific people?}
    \end{itemize}
\end{itemize}

\textbf{Interaction with anothers posts}\\
A post will typically be displayed on the newsfeeds of the people who are able
to see it, due to this the name of the person who made a post is always
displayed next to it. Posts themselves may be commented upon, liked, and
reposted to the viewers wall ('shared') with an additional message; the number
and names of people who have liked a post is displayed underneath it; likes may
be cancelled at a later date. The comment function may however be disabled by
the user who makes a post.

A user may hide specific posts, or hide all posts by a specific user. They may
also, instead of hiding anothers posts alltogether, merely prevent them from
being automatically displayed on their newsfeed. \todo{See 72d5e2dc, what
is 'set a notification'?} A user may report an image, video or comment to
facebook team (for example:the post is offensive). Comments may also be liked,
hidden, and reported; following such a report FB is able to remove offensive or
illegal posts. \todo{allow user to share the post on third-party web(e.g.
YouTube, Steam information): really? I don't remember seeing this option in
steam}

Images which are posted may be tagged, this allows other users to mouse-over
parts of the image and be informed who is pictured. This functionality is also
used to add all posted images of someone to their profile.
