\section{Registration}
Users may register by sending a CLAIM message to the server, this will claim a
username for that user, and allow people they send messages to to see their
username.

Before registering the user must generate an RSA keypair, they will be given the
option of generating a new keypair, or using an existing keypair. The keypair
provided will be encrypted using AES with the users password being used to
derive the key. The user therefore must enter their password to log into the
client. The database will be encrypted using the same AES key as the keys are
encrypted with.

\section{Interacting with other users}
People are added by adding their public key, this is transmitted outside of our
system, via whichever channel the users deem appropriate\footnote{This is
required to prevent server operators from MitM'ing users}. We will provide a
user with their public key as a QR code, or a plaintext string, depending on
user preference.

Adding someone is asymmetric. Just because you add them doesn't mean they've
added you. You do not require consent to add someone, just their public key.
    
The system allows the user to manage their list of known people into categories
such as friends, family, and co-workers. The user defines these groups as lists
of people whose public key they know. The user may create any group they desire,
these groups are visible to only the user, and private.

\section{Profile Data}
Profile data will be transmitted via PDATA messages. Different versions of
profile information may be provided to different groups of people. Profile data
may be updated by the user by future PDATA messages.

The supported fields in a PDATA message are:
    \begin{itemize}
        \item Name
        \item Username (unique, but this uniqueness is ensured by server and
              shouldn't be relied on)
        \item Birthday
        \item Sex
        \item E-Mail
        \item About
    \end{itemize}

\section{Account recovery}
Account recovery is not possible without your keypair, due to this the the GUI
should urge the user to keep a copy on a flash drive, or external hard drive.
The keys themselves will be encrypted with the users password.

\section{Posts}
\subsection{Walls}
Each user has their own wall. On their wall they may posts messages for
themselves and others to see. All wall posts should be addressed to the user
themselves so they can see their own posts, otherwise they will be unable to even
view their own posts. When posting to their wall they choose who will be able to
see the post, whether this is a group or people, a specific list of people, or
just themselves is up to the user. They will not however be given the option to
post publicly. Users may also post to another users wall.

Wall posts may contain links to other content, however this content is never
thumb-nailed\footnote{client MUST NEVER thumbnail links or otherwise access
external content without EXPLICIT user consent (see tor/js exploit on freedom
hosting by the USA and tracking techniques recently thwarted by GMail now
caching images. Specifically the fact that by delivering content over a secure
channel that initiates communications outside of that channel, the recipients of
content may be identified. A common variation of this is 'pixels' whereby a
would be tracker embeds a 1x1 transparent .png in a document, and watches who
downloads that image from their servers.\cite{webbug}}.

A user may edit their old posts, however older versions will still be available
for viewing; similarly users may 'delete' posts, but they are still visible to
malicious clients.

Due to bandwidth limitations on such networks as we are building, a user may
only post plaintext, they may not post images, video, or audio.

\subsection{Commenting and Liking}
All wall posts may be commented on by any user who can see them. Comments are
visible to all people who can see the original post; due to this, comments must
be forwarded by the original posters client to all the same recipients, as the
commenter may not know whom the original posters allowed to see the post.

Any wall post, comment, or other item on a wall may be liked.
    
\subsection{Events}
The client will alert the user to other users birthdays by automatically posting
a wall post that only the user may read, which alerts the user of the event.
These are otherwise normal wall posts.

The user has the option of setting a category of people as people for whom they
desire to be alerted of events regarding.

\section{Chat}
Users may chat in real time, however messages can still be sent when one user
logs off, to be received when they log in. Past conversations are saved, and a
user may block users from messaging them; the client actually just ignores their
messages, it's impossible to stop someone from messaging you.
