
\section{presonal information}

User can manage there account , what presonal information they want to show to public .
all the presonal information,  that user wants to show will contain on "About".User have option to hide all the information .

following information will contain in "About"

\begin{itemize}

\item Work and education

\item PLece Lived

\item Relationship

\item Basic Information
	\begin{itemize}
		\item Birthday
		\item Relaionship
		\item Status
		\item Anniversary
		\item Languages
		\item Religious
		\item Political
		\item Family
		\item Contact Information
	\end{itemize}

\item photo 
	\begin{itemize}
	\item all the photo have user's taged 
	\end{itemize}

\item Friends
	\begin{itemize}
	\item what friend user had
	\end{itemize}

\item Note
	\begin{itemize}
	\item What Notes user droped and uploaded to facebook .
	\end{itemize}

\item Groups
	\begin{itemize}
	\item What group have user join.
	\end{itemize}

\item Events
	\begin{itemize}
	\item what Events user have.
	\end{itemize}

\item Likes
	\begin{itemize}
	\item what page(unknow type) user liked.
	\end{itemize}

\item Apps
	\begin{itemize}
	\item what apps user have.
	\end{itemize}

\item Books
	\begin{itemize}
	\item what books page user liked/follow.
	\end{itemize}

\item TV programmes
	\begin{itemize}
	\item what TV page user liked/follow.
	\end{itemize}

\item Films
	\begin{itemize}
	\item What Films page user Liked/follow.
	\end{itemize}

\item Music
	\begin{itemize}
	\item what Music(or stars) user liked/ follow.
	\end{itemize}

\item Sports
	\begin{itemize}
	\item -what sport page user liked.
	\end{itemize}

\item Place
	\begin{itemize}
	 \item -where's the place that user had been .
	 \end{itemize}
