\section{Included Works}
Despite them being present in the repo, we did not write or create the following:
\begin{itemize}
\item writeup/latex/tikz-uml.sty
\item writeup/latex/todonotes.sty
\item writeup/latex/ulem.sty
\item tikz-styles.sty
\item writeup/images/appendicies/licence.png (CC0 licence logo)
\item The text of any legal licence
\item client/web\_interface\_mockup/jquery.js
\item client/web\_interface\_mockup/turtles.ttf
\end{itemize}

\section{The turtle image used as a favicon and in the banner}
This was dedicated to the public domain by its creator. The UK both is a
signatory of the berne convention and has precedent holding that licencing
cannot be retroactivly rescinded.

\section{jquery.js Licence}
Copyright 2014 jQuery Foundation and other contributors
http://jquery.com/

Permission is hereby granted, free of charge, to any person obtaining
a copy of this software and associated documentation files (the
"Software"), to deal in the Software without restriction, including
without limitation the rights to use, copy, modify, merge, publish,
distribute, sublicense, and/or sell copies of the Software, and to
permit persons to whom the Software is furnished to do so, subject to
the following conditions:

The above copyright notice and this permission notice shall be
included in all copies or substantial portions of the Software.

THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND,
EXPRESS OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF
MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE AND
NONINFRINGEMENT. IN NO EVENT SHALL THE AUTHORS OR COPYRIGHT HOLDERS BE
LIABLE FOR ANY CLAIM, DAMAGES OR OTHER LIABILITY, WHETHER IN AN ACTION
OF CONTRACT, TORT OR OTHERWISE, ARISING FROM, OUT OF OR IN CONNECTION
WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE SOFTWARE.

\section{todonotes.sty licence}
Copyright (c) 2008 by Henrik Skov Midtiby <henrikmidtiby@gmail.com>

This file may be distributed and/or modified under the conditions of the LaTeX
Project Public License, either version 1.2 of this license or (at your option)
any later version. This licence is provided below.

\input{text/appendicies/latexppl.tex}

\section{CC0 licence and licence.png licence}
The CC0 licence and the licence.png image is licenced under the creative commons
attribution international 4.0 licence, this is provided below (NB: This licence
is licenced under itself.)

\input{text/appendicies/by4i.tex}

\section{ulem.sty licence}
Copyright (c) 1989-2011 by Donald Arseneau (Vancouver, Canada; asnd@triumf.ca)

This software may be freely transmitted, reproduced, or modified for any purpose
provided that this copyright notice is left intact. Small excerpts may be taken
and used without any restriction.)

\section{tikz-uml.sty licence}
tikz-uml.sty is licenced under the LPPL, previously given.

\section{tikz-styles.sty licence}
tikz-styles.sty is licenced under the LPPL, previously given.

\section{sqlite-jdbc-3.7.2.jar licence}
sqlite-jdbc-3.7.2.jar is licenced under the Apache License version 2.0.
\input{text/appendicies/apache2.tex}

\section{winstone.jar licence}
Winstone is licenced under the CDDL.
\input{text/appendicies/cddl.tex}

\section{CDDL licence licence}
The CDDL is not the creation of BallmerPeak but was created by Sun Microsystems.
The CDDL is licenced under CC Attribution 3.0 Unported. Fortunatly CC-BY-3
allows merely linking to it, the licence can be found here:
http://creativecommons.org/licenses/by/3.0/legalcode

\section{Unlicenced Material}
The following are reproduced and distributed without permission.
\begin{enumerate}
\item The text of the IP policy of The University of Liverpool
\end{enumerate}
