Ballmer Peak is the team behind Turtlenet, both its designers and creators.
We have worked together over the past 6 months to create a new, innovative 
product the entire team is proud of. Pooling our resources and individual
technical skills we feel we came together as a team and produced a quality
product. We all had our roles to fill in this project:

\section{Peter Duff - Team Lead}
\begin{itemize}
\item In charge of project management and organisation, as well as assigning roles and 
responsibilities, amongst other generic managerial admin.
\item Was the designer and creator of the Turtlenet website.
\item Proofreader of the entire requirements, design and portfolio documents.
\end{itemize}

\section{Luke Thomas - Lead Programmer}
\begin{itemize}
\item Designed and created the initial prototype and idea for the project.
\item Wrote the whole of the client, except for Database.java, DBStrings.java, and frontend.java. Significantly contributed to Database.java and frontend.java.
\item Wrote the whole of the server.
\item Wrote the automated tests, designed \LaTeX{} documents.
\end{itemize}

\section{Louis Prince - Programmer}
\begin{itemize}
\item Programmed and designed the GUI for the client (frontend.java).
\item Redesigned parts of the Turtlenet website.
\end{itemize}

\section{Aishah Senin - Database Developer}
\begin{itemize}
\item Documented all aspects of the database.
\item Designed and created the SQLite database from scratch.
\item Wrote database queries.
\end{itemize}

\section{Michael Chadwick - Software Engineer}
\begin{itemize}
\item Wrote the majority of the user manual for the program.
\item Provided heavy documentation regarding some of the finer, non-technical
points of the project (Gantt, Risk Asses. etc.).
\item Wrote a significant portion of Database.java
\end{itemize}

\section{Leon Choi - Researcher}
\begin{itemize}
\item Main researcher into existing similar systems and potential future work.
\item Designed a mock GUI for future android work.
\item \ldots \todo{Think of something, the GUI was never connected to the server and never came close to working. Other server functionality like DDOS mitigation was never done because we were waiting on the GUI before assinging more functionality.}
\end{itemize}
