\begin{enumerate}
\item We have decided that the event function isn't very valuable and so dropped it
from the requirements early in development.

\item Our data flow has changed in that the client now updates the local
database without waiting for updates from the server to arrive. This was done so
that network latency didn't interfere with the user experiance. All actions are
still sent to oneself via the server, else multiple clients with the same key
wouldn't function.

\item The client-client protocol has been significantly expanded so that all
actions can be represented within it. This is so that if all one has is a
keypair to an account, that account may be fully recovered. An example of new
functionality in the protocol is that category creation and modification is
recorded on the server (via encrypted messages sent, and viewable, soley to
oneself). NB: The client-server protocol is wholly unaltered.

\item The datatypes in the database have changes due to the limitations of
SQLite.

\item The primary key in many database tables has changed from an arbitrary
value to a globally identifying cryptographic signature (from the message
establishing the relevent datum.)

\item A number of accessors were added to the Message class for extracing
information from different types of messages.

\item The DBStrings class was added so as to keep SQL query strings seperate
from java code, and to localize them within one namespace. This class merely
contains a large number of static strings.

\item The Logger, Tokenizer,  MessageFactory, and F(ile)IO class were added as
helper classes. Tokenizer was created instead of using javas existing Tokenizer
class because we needed a tokenizer automatically convertable to javascript. A
factory class was required because the Message class cannot contain constructors
not automatically convertable to javascript.

\item The following data bearing classes were created to return structured data
to the HTML/JS frontend. They allow the more powerful java backend to extract
(and format) data from the database before returning a simple class containing
it.
\begin{enumerate}
\item Friend
\item CommentDetails
\item Conversation
\item PostDetails
\end{enumerate}

\item The Turtlenet, TurtlenetImpl, and TurtlenetAsync classes exist to provide
an asynchronous interface between the HTML/JS frontend and the Java backend.
\end{enumerate}
