\begin{enumerate}
\item Lack of communication
Communication is highly important when working as a team. It allows team members 
to be aware on what is happening as a whole on the project at hand. Despite working 
on one area of a project, there are always some areas where there is a need to 
integrate the work to other areas, and this is when communication comes in handy. 
Team members are also expected to keep each other updated frequently regarding 
the progress of the project so no one is left behind. Other reasons why communication 
is vital is ideas can come from different members, making sure that these ideas are 
reached out and heard and possibly put into account brings team members to feel 
appreciated and important. 

\item Being open towards one another
There will always be a fallout between teams over time. To avoid that, team members 
are advised to be open towards others especially when there is a problem on certain 
areas. Criticism is encouraged, but as are good manners.

\item Handling of non-team players
What can the other team members do when someone in the team exhibits such behaviour? 
One way is to encourage the team member to modify his or her behaviour for the sake of 
others. Inform the person regarding the reason why we are working as a team, and 
changing such behaviour might benefit the team as a whole. Team members who displays 
such behaviour may create negative feelings from other team members which is not healthy 
for the relationship of the team.
\end{enumerate}